One Model May Not Fit All: Subgroup Detection Using MOB

### 2023-10-11 Raschtree_MH.Rnw
Comments about changes

@@

<<echo = FALSE>>=
load("SPISA_example/dat_SPISA.rda")
covar_data$Student <- NULL
covar_data$Occupation <- NULL
@

@@

>>>>

\todo[inline]{Comment on new example: I now use data from Bogen 20 of the SPISA dataset. I use the student subset, and complete cases on all variables. The story is less clear, but the tree is still stopped early, and we can display which items have dif. }

@@

<<echo = FALSE>>=
load("SPISA_example/dat_SPISA.rda")
covar_data$Student <- NULL
covar_data$Occupation <- NULL
covar_data$Area <- sub("\n", "", covar_data$Area)
@

@@

\todo[inline]{The are covariate split does not look pretty yet. But I will try to make it more pretty later on.. }
